Empirical Evaluation of eval in R

### 2020-08-25 inst/analysis/analysis_stable.Rmd
Fix usage of ratio

r("percent parsed evals",  ratio(nb_parsed_evals, nb_eval_calls))
```

@@

r("paste parsed evals", ratio(nb_meta_parsed, nb_parsed_evals))
r("paste parsed call site", ratio(nb_meta_parsed_call_sites, nb_parsed_call_sites))
```

>>>>

r("percent parsed evals",  ratio(nb_parsed_evals$n, nb_eval_calls))
```

@@

r("paste parsed evals", ratio(nb_meta_parsed$n,  nb_parsed_evals$n))
r("paste parsed call site", ratio(nb_meta_parsed_call_sites,  nb_parsed_call_sites))
```
